---
title: "03_decision_data"
author: "Laura Botzet, Sarah Forsthoff, Tanja Gerlach"
date: "20 April 2018"
output:
  html_document
---

# Dataset Decision {.tabset}

## Library
```{r, warning=FALSE, echo=FALSE, results = 'hide', include = FALSE}
# library(jsonlite)
# install.packages("devtools")
# devtools::install_github("rubenarslan/formr")
 library(formr)
# library(psych)
# library(stringr)
library(mosaic)
library(tidyr)
library(apaTables)
library(dplyr)
```

## Data Import
```{r}
data = read.csv(file = "ImportedData/data.csv")
```

## Detect possible liars
```{r}
# Create Liar Variable
data = data %>%
  mutate(check_relationship_liars_all = ifelse(as.Date(created_t1) < as.Date(start), 0, 1),
         check_relationship_liars_exclusive = ifelse(check_relationship_liars_all == 1 & kind == 1, 1, 0))

# Create Liar Vector
liars_all = data %>% filter(check_relationship_liars_all == 1) %>% select(session)
liars_all = as.vector(liars_all$session)

liars_exclusive = data %>% filter(check_relationship_liars_exclusive == 1) %>% select(session)
liars_exclusive = as.vector(liars_exclusive$session)

# Mark people as liars
data = data %>%
  mutate(check_liars_all = ifelse(session %in% liars_all, 1, 0),
         check_liars_exclusive = ifelse(session %in% liars_exclusive, 1, 0))
``` 

## Different Dataset Possibilities {.active .tabset}
### Sample Sizes {.active .tabset}
#### Full Sample
```{r}
# Full Data
n_relationships = data %>% filter(lasting != 0) %>% count()
n_participants = data %>% filter(!duplicated(session)) %>% count()
n_partner = data %>% filter(!duplicated(session)) %>% filter(lasting != 0) %>% count()
n_single = data %>% filter(lasting == 0) %>% count()

```

The full sample includes `r n_participants` participants:

* `r n_single` Singles

* `r n_partner` who report a relationship with overall `r n_relationships` relationships

#### Restriced Sample (no Liars)

```{r}
# Exclude Liars
n_relationships_nonliars = data %>% filter(check_liars_all == 0) %>% count()
n_participants_nonliars = data %>% filter(check_liars_all == 0) %>% filter(!duplicated(session)) %>% count()
n_partner_nonliars = data %>% filter(check_liars_all == 0) %>% filter(!duplicated(session)) %>%
  filter(lasting != 0) %>% count()
n_single_nonliars = data %>% filter(check_liars_all == 0) %>% filter(lasting == 0) %>% count()
```

The restricted sample includes `r n_participants_nonliars` participants:

* `r n_single` Singles

* `r n_partner_nonliars` who report a relationship with overall `r n_relationships_nonliars` relationships

#### Restriced Samples (exclude exclusive Liars)
```{r}
n_relationships_nonliars_exclusive = data %>% filter(check_liars_exclusive == 0) %>% count()
n_participants_nonliars_exclusive = data %>% filter(check_liars_exclusive == 0) %>%
  filter(!duplicated(session)) %>% count()
n_partner_nonliars_exclusive = data %>% filter(check_liars_exclusive == 0) %>% filter(!duplicated(session)) %>%
  filter(lasting != 0) %>% count()
n_single_nonliars_exclusive = data %>% filter(check_liars_exclusive == 0) %>% filter(lasting == 0) %>% count()

```

The restricted sample based on exclusive relationships at t1 includes `r n_participants_nonliars_exclusive` participants:

* `r n_single` Singles

* `r n_partner_nonliars_exclusive` who report a relationship with overall `r n_relationships_nonliars_exclusive` relationships

#### Restriced Samples (only commited relationships; exclude exclusive Liars) {.active}
```{r}
data_commited = data %>% filter(is.na(kind) | kind == 1)
n_relationships_commited = data_commited %>% filter(check_liars_exclusive == 0) %>% count()
n_participants_nonliars_commited = data_commited %>% filter(check_liars_exclusive == 0) %>%
  filter(!duplicated(session)) %>% count()
n_partner_nonliars_commited = data_commited %>% filter(check_liars_exclusive == 0) %>% filter(!duplicated(session)) %>%
  filter(lasting != 0) %>% count()
n_single_nonliars_commited = data_commited %>% filter(check_liars_exclusive == 0) %>% filter(lasting == 0) %>% count()

```

The restricted sample based on on comitted relationships and excluding liars at t1 includes `r n_participants_nonliars_commited` participants:

* `r n_single` Singles

* `r n_partner_nonliars_commited` who report a relationship with overall `r n_relationships_commited` relationships

## Potential Problems with including Liars

Including liars comes with the following diasadvantages:

* we do not know whether they were really single at t1

* we do not know the real ending of their last relationship, thus we could not calculate a good survival analysis

* it is not possible to exclude only the wrong relationship because it messes up all following analyses
