---
title: "04_exanalyses"
output: html_document
---

```{r}
library(survival)
library(coxme)
library(survminer)
```


Data: merged data from t1, t2, t3
```{r}
surv_data <- data_exclusive_clean

surv_data <- surv_data %>%
  filter(!sex == 3)
```


#Analyses of relationship start

##Prepare data for cox function
```{r}
#Set the start of being single for all participants to zero
surv_data <- surv_data %>% mutate(
  single_start_d = 0)

#Now we calculate the time until the entry in a relationship with the starting date of the relationship
surv_data$start <- as.Date(surv_data$start)
surv_data <- surv_data %>% mutate(
  relationship_start_d = start - single_start) %>% #still negative values, needs further checking, approx. 10
  filter(relationship_start_d > -1 | is.na(relationship_start_d))

```

##Sex as Predictor
```{r}

surv_data$sex <- factor(surv_data$sex, levels = c("1","2"))

start_sex.1 <- survfit(Surv(single_start_d, relationship_start_d, event) ~ sex, data = surv_data)
summary(start_sex.1)
plot(start_sex.1, mark.time = T, col = c("blue","red"), conf.int = F)
ggsurvplot(start_sex.1, data = surv_data, conf.int = T)

start_sex.2 <- survfit(Surv(single_start_d, relationship_start_d, event) ~ sex + cluster(session), data = 
                         surv_data)
summary(start_sex.2)
plot(start_sex.2, mark.time = T, col = c("blue","red"), conf.int = F)
ggsurvplot(start_sex.2, data = surv_data, conf.int = T)
```

##Age as Predictor
```{r}
start_age.1 <- survfit(Surv(single_start_d, relationship_start_d, event) ~ age + cluster(session), data = 
                         surv_data)
summary(start_age.1)
ggsurvplot(start_age.1, data = surv_data, conf.int = T)

```

##Narcissism as Predictor
```{r}
##as continous 
#with coxph for continous predictor
start_narq_con.1 <- coxph(Surv(single_start_d, relationship_start_d, event) ~ NARQ_scale + cluster(session), data =
                            surv_data)
summary(start_narq_con.1)
plot(survfit(start_narq_con.1))

#with survfit function
start_narq_con.2 <- survfit(Surv(single_start_d, relationship_start_d, event) ~ NARQ_scale + cluster(session), data
                            = surv_data)
summary(start_narq_con.2)
ggsurvplot(start_narq_con.2, data = surv_data, conf.int = T)


##as groups

median_NARQ_scale = median(surv_data$NARQ_scale, na.rm = T)
surv_data = surv_data %>%
  mutate(NARQ_group = ifelse(NARQ_scale <= median_NARQ_scale, "low", 
                             ifelse(is.na(NARQ_scale), NA, "high")),
         NARQ_group = as.factor(NARQ_group))


start_narq_gr <-  survfit(Surv(single_start_d, relationship_start_d, event) ~ NARQ_group + cluster(session), data
                            = surv_data)
summary(start_narq_gr)
ggsurvplot(start_narq_gr, data = surv_data, conf.int = T)

```

##Admiration as Predictor
```{r}
median_NARQ_ADM = median(surv_data$NARQ_ADM, na.rm = T)

surv_data = surv_data %>%
  mutate(NARQ_ADM_group = ifelse(NARQ_scale <= median_NARQ_ADM, "low", 
                             ifelse(is.na(NARQ_scale), NA, "high")))
                             

start_ADM_gr <- survfit(Surv(single_start_d, relationship_start_d, event) ~ NARQ_ADM_group + cluster(session), data = surv_data)
summary(start_ADM_gr)
ggsurvplot(start_ADM_gr, data = surv_data, conf.int = T)
```




#Analyses of relationship end
    Create necessary variables: relationship_start_d_end, relationship_end_d, event_end
```{r}
#create sub data: including only participants with at least one relationship
surv_data_rel <- data_exclusive_clean %>% filter(!is.na(kind))

surv_data_rel <- surv_data_rel %>% mutate(
  relationship_start_d_end = 0, #Do we set the start of the relationship to O, similiar to the beginning of being                                   single above?
  relationship_end_d = end - start) %>%
  filter(relationship_end_d > -1 | is.na(relationship_end_d))

```


##Sex as Predictor
```{r}

surv_data_rel$sex <- factor(surv_data_rel$sex, levels = c("1","2"))

end_sex.1 <- survfit(Surv(relationship_start_d_end, relationship_end_d, event_end) ~ sex, data = surv_data_rel)
summary(end_sex.1)
plot(end_sex.1, mark.time = T, col = c("blue","red"), conf.int = F)
ggsurvplot(end_sex.1, data = surv_data_rel, conf.int = T)

end_sex.2 <- survfit(Surv(relationship_start_d_end, relationship_end_d, event_end) ~ sex + cluster(session), data =
                       surv_data_rel)
summary(end_sex.2)
plot(end_sex.2, mark.time = T, col = c("blue","red"), conf.int = F)
ggsurvplot(end_sex.2, data = surv_data_rel, conf.int = T)
```

##Age as Predictor
```{r}
end_age.1 <- survfit(Surv(relationship_start_d_end, relationship_end_d, event_end) ~ age + cluster(session), data =
                       surv_data_rel)
summary(end_age.1)
ggsurvplot(end_age.1, data = surv_data_rel, conf.int = T)

```

##Narcissism as Predictor
```{r}
##as continous 
#with coxph for continous predictor
end_narq_con.1 <- coxph(Surv(relationship_start_d_end, relationship_end_d, event_end) ~ NARQ_scale + 
                          cluster(session), data = surv_data_rel)
summary(end_narq_con.1)
plot(survfit(end_narq_con.1))

#with survfit function
end_narq_con.2 <- survfit(Surv(relationship_start_d_end, relationship_end_d, event_end) ~ NARQ_scale + 
                            cluster(session), data = surv_data_rel)
summary(end_narq_con.2)
ggsurvplot(end_narq_con.2, data = surv_data_rel, conf.int = T)


##as groups

median_NARQ_scale = median(surv_data_rel$NARQ_scale, na.rm = T)
surv_data_rel = surv_data_rel %>%
  mutate(NARQ_group = ifelse(NARQ_scale <= median_NARQ_scale, "low", 
                             ifelse(is.na(NARQ_scale), NA, "high")),
         NARQ_group = as.factor(NARQ_group))


end_narq_gr <-  survfit(Surv(relationship_start_d_end, relationship_end_d, event_end) ~ NARQ_group + cluster(session), data
                            = surv_data_rel)
summary(end_narq_gr)
ggsurvplot(end_narq_gr, data = surv_data_rel, conf.int = T)

```

##Admiration as Predictor
```{r}
median_NARQ_ADM = median(surv_data_rel$NARQ_ADM, na.rm = T)

surv_data_rel = surv_data_rel %>%
  mutate(NARQ_ADM_group = ifelse(NARQ_scale <= median_NARQ_ADM, "low", 
                             ifelse(is.na(NARQ_scale), NA, "high")))
                             

end_ADM_gr <- survfit(Surv(relationship_start_d_end, relationship_end_d, event_end) ~ NARQ_ADM_group + 
                        cluster(session), data = surv_data_rel)
summary(end_ADM_gr)
ggsurvplot(end_ADM_gr, data = surv_data_rel, conf.int = T)
```


